### 2017-04-08 Manuscripts/cog-psych/cogpsych.tex
drafted jk13 analysis section

\nbcnote{Report analyses on the \cite{jern2013probabilistic} data here...}

>>>>

Participants in their experiment were exposed to members of two experimenter-defined categories of `crystals' varying in hue, saturation, and size. Each category possessed a unique hue, but varied in saturation and size: In the `Positive' condition, there was a positive correlation between these features (i.e., larger sized crystals were more saturated), and in the `Negative' condition this relation was reversed. In the `Neutral' condition, there was no correlation between saturation and size. After learning about the categories from each condition, participants were asked to generate six exemplars belonging to a novel class. As noted above, \cite{jern2013probabilistic} found that the generated categories tended to follow the distributional properties of the experimenter-defined categories: generated categories were tightly distributed along the hue feature, and possessed the same saturation-size correlations as in the learned categories. \cite{jern2013probabilistic}, however, did not provide an analysis of how the generated categories \textit{differed} from the experimenter-defined categories. Here, we provide such an analysis.

Because each experimenter-defined category in the \cite{jern2013probabilistic} experiment possessed a distinct hue, it is sensible to propose that participants would make their generated category distinct along this feature as well. Problematically, however, stimulus hue was measured on an circular (HSV) scale with limits $[0,1]$: both 0 and 1 corresponded to a `red' hue, and all other hues were represented between these values. By consequence, proximity on this dimension does not directly correspond to perceptual similarity. To overcome this issue, we categorized the hues of each participant's generated categories into one of six uniformly-spaced color groups: \{\textit{red}: 0 \& 1, \textit{yellow}: 0.167, \textit{green}: 0.333, \textit{teal}: 0.5, \textit{blue}: 0.667, \textit{pink}: 0.833\}. After each example's hue was categorized, we computed the amount of overlap between the hues of the six examples generated by each participant and the two hues possessed by the experimenter-defined categories. If contrast influences the hues of the generated categories, we should observe minimal overlap between the generated and experimenter-defined categories.

\nbcnote{Joe should probably do a pass through that language. Maybe add a cite for proximity-similarity distinction?}

\begin{figure}
    \begin{center}
        \inputpgf{figs/}{jk13-huecontrast.pgf}
        \caption{Analysis of data from \cite{jern2013probabilistic}, Experiment 3. Plotted is the number of generated items that share a color group with one of the experimenter-defined classes. The ``Expected'' data follows a Binomial distribution with $p=2/6$, given there were two experimenter-defined classes, and 6 color groups.}
        \label{fig:jk13-huecontrast}
    \end{center}
\end{figure}

These data, shown in Figure \ref{fig:jk13-huecontrast}, reveal a clear pattern: The majority of participants generated categories possessing entirely distinct hues--with 0/6 exemplars sharing a hue with the experimenter-defined categories. These results can be compared to the predictions of a Binomial model, which proposes that participants generate hues at random. According to the model, if participants had generated hues at random, the probability that any given example will lie in the same color group as an experimenter-defined category is $p = 2/6$, as there were two experimenter-defined categories and six possible color groups. Thus, the number of shared hues is Binomially distributed with $p=2/6$ and $n=6$ (as that participants generated six examples in each condition). Comparison of \cite{jern2013probabilistic}'s results to the model's predictions reveals participants were far more likely to select distinct hues: participants tended to generate items that were perceptually distinct from the categories they had learned.

\nbcnote{Some wrap-up ...}
